DisCon Kids Pilot

### 2019-03-14 analysis/02_kids_6v1.Rmd
analysis pipeline 6v1

---
title: "DisCon Kids Pilot"
output: html_document
  code_folding: hide
---

@@

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/600/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/600/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

p2 <- p1 %>%
  group_by(experiment) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

# Proportion correct choice in test trials by age bin

```{r proportion of choices}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

p4 <- p3 %>%
  group_by(subage) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized(name = "Age")
```

Proportion correct choice by age continous

```{r}
p5 <- data %>%
  filter(phase == 'test')%>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

# Bayesian t-test against chance across age groups

```{r}
## one sample bayesian t-tests
library(BayesFactor)

data %>%
  filter(phase != "training") %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(mean,bf) %>%
  knitr::kable(digits = 3)

# Bayesian t-test by age group

```{r}
## one sample bayesian t-tests
library(BayesFactor)

data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(subage,mean,bf) %>%
  knitr::kable(digits = 3)

```
Plotting posterior based on t-test

```{r}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

plot_dens_ci <- plot_post %>%
  summarise(mode = estimate_mode(unlist(posterior)),
            lci = hdi_lower(unlist(posterior)),
            uci = hdi_upper(unlist(posterior)))

#### make density plot ?

plot_dens <- data_frame(
  age = rep(c(3,4), each = 1000),
  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)

densities <- plot_dens %>%
  group_by(age) %>%
  do(., dens = density(.$posterior))

densities_df <-
  data.frame(
    age = c(rep('3', 512),
              rep('4', 512)),
    x = c(densities$dens[[1]]$x, 
          densities$dens[[2]]$x),
    y = c(densities$dens[[1]]$y,
          densities$dens[[2]]$y)
  ) %>%
  group_by(age)%>%
  mutate (
    ci_shade = ifelse( age == "3",
      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))

ggplot(plot_dens, aes(posterior, group = factor(age))) +
  geom_density(alpha = .5)+
  geom_vline(xintercept = 1/3, lty=2)+
  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
  labs(x="Proportion Correct")+
  theme_few() +
  xlim(-0.05,1.05)+
  guides(alpha = F)+
  scale_fill_solarized(name = "Age")+
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

# Comparison to chance based on model

```{r}
chance_data <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  mutate(comp_chance= ifelse(correct<1/3,0,1))

library(brms)

chance_model <- brm(comp_chance ~ 1,
                    data = chance_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(chance_model)

```{r}
bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

@@

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

ggplot() +
  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

## position effects
```{r proportion of choices}
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(correct = mean(correct_target1))

pos_plot_mean <- pos_plot %>%
  group_by(pickPos) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pos_plot, aes(x = pickPos, y = correct,  alpha = .2, col = pickPos),width = .2,height = .01)+
  geom_pointrange(data = pos_plot_mean, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper, col = pickPos),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

>>>>

---
title: "DisCon Children 6 vs. 1 exposure trials"
output: html_document
  code_folding: hide
---

@@

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/6v1/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/6v1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d6v1")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F), 
         distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(distribution,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

p2 <- p1 %>%
  group_by(distribution) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = distribution, y = correct, col = distribution), alpha = .2 ,width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = distribution),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

kbm1 <- brm(correct_target1 ~ age_num * distribution
                      (condition| subid) + (condition | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ age_num +
                      (condition| subid) + (condition | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

ggplot() +
  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F)+
  scale_color_solarized()
```

## position effects
```{r }
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(n = n())%>%
  group_by(pickPos)%>%
  multi_boot_standard(col = "n")

ggplot() +
  geom_pointrange(data = pos_plot, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
   labs(x="Item position",y="Mean item in this position chosen at test")+
  theme_few() +
  ylim(0,4)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

# one sample wilcoxon
```{r}

# Based on: http://ipg.idsia.ch/preprints/benavoli2014a.pdf
source("../scripts/isignrank.test.R")

rank_data <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  mutate(chance = rep(1/3,length(correct)))

isignrank.test(rank_data$chance,rank_data$correct,"two.sided")

# Based on : https://arxiv.org/pdf/1712.06941.pdf
source("../scripts/signRankSampler.R")

rank_test <- signRankGibbsSampler(rank_data$correct,rank_data$chance)

rank_test_plot <- data.frame(rank_test)

ggplot(rank_test_plot, aes(plogis(deltaSamples))) +
  geom_density(alpha = .5)+
  xlim(0,1)
```

### 2019-03-14 analysis/02_kids_pilot.Rmd
analysis pipeline 6v1

>>>>

# 2yo in 600

```{r data pre-processing, include = F}

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/pilot/600/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/pilot/600/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

```{r proportion of choices}
pos_plot <- raw_data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(n = n())

pos_plot2 <- pos_plot%>%
  group_by(pickPos)%>%
  multi_boot_standard(col = "n")

ggplot() +
  geom_jitter(data = pos_plot, aes(x = pickPos, y = n, col = subid),size = 2, height = 0, alpha = 1)+
  geom_hline(yintercept = 4/3, lty=2)+
  geom_pointrange(data = pos_plot2, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  labs(x="Item position",y="Mean number of times item was chosen")+
  theme_few() +
  ylim(0,4)+
  guides(alpha = F)+
  scale_color_ptol()
```

```{r}
p1 <- raw_data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  group_by(experiment) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```
